\makeglossaries

% Acronyms
% Follow the form: \newacronym{label}{ACRONYM}{expansion}
\newacronym{caida}{CAIDA}{Center for Applied Internet Data Analysis}
\newacronym{aws}{AWS}{Amazon Web Services}
\newacronym{fcc}{FCC}{Federal Communications Commission}
\newacronym{gps}{GPS}{global positioning system}
\newacronym{ip}{IP}{internet protocol}
\newacronym{isp}{ISP}{internet service provider}
\newacronym{ripe}{RIPE}{R\'eseaux IP Europ\'eens}
\newacronym{rtt}{RTT}{round trip time}
\newacronym{dns}{DNS}{domain name system}
\newacronym{voip}{VoIP}{voice over internet protocol}
\newacronym{mbps}{Mbps}{megabits per second}

% Acronyms with definitions
% Follow the form: \newacronym{label}{ACRONYM}{expansion}{description}. Description appears in glossary only.
 \newacronym{cdn}{CDN}{content delivery network}{A Content Distribution Network (CDN), sometimes called a Content Delivery Network, is a network of proxy servers that form a kind of cache used to enhance delivery of content to internet users. Although helpful for internet users, they complicate measurements of connectivity to websites \textit{actually} connecting to the site's servers}
 
 \newacronym{icmp}{ICMP}{internet control message protocol}{Internet Control Message Protocol (ICMP) is a protocol designed for error reporting and other utility purposes across the internet, typically used most by routers and other intermediary devices. By setting a TTL lower than the number of hops to the destination, you can force a device along the route to send back a TTL-expired message, revealing the server's presence along the route. This is in essence how traceroutes work}
 
 \newacronym{cv}{CV}{coefficient of variance}{Coefficients of variance (CVs) are calculated by dividing the standard deviation of a data set by its mean. CVs are dimensionless values that can be judged independent of the data set, making them useful for gauging the spread of any data set. The lower the CV, the lower the spread of the data and the better the quality}
 

% Glossary entries -- these should be more detailed.
% Follow the form: \newglossaryentry{LABEL}{name={NAME} description={YOUR TEXT HERE}}
\newglossaryentry{favicon}{
    name={favicon},
    description={Favicons are small identifying images, typically logos or relevant UI elements, that most websites provide for browsers to place on tabs and bookmarks. Favicons are stored as .ico files (icons) and are either 16x16, 32x32, or 48x48. This small size makes them ideal for testing connection \glspl{rtt} from a browser}
}

\newglossaryentry{backbone}{
    name={internet backbone},
    description={Internet backbone infrastructure consists of very high speed principal data routes and the connected major computer networks and core routers. For any trip of serious distance (likely most connections, unless you happen to have a data center in your backyard), packets will inevitably pass through some element of the internet backbone}
}
